### 2017-06-13 KineticModel/estimation/docs/formulation/noisy_estimate.tex
changes made to forumaltion based on scip results

	The optimization formulation to estimate fluxes given below is based on the minimization of the tolerance for the L2-norm of the difference between the model predicted flux and the noisy flux. 
	\begin{center}
		\begin{subequations}\label{eq:noisyopt}
			\begin{align}
			\underset{x,p}{\mathrm{min}} & \text{      }e\\
			\mathrm{st} & \text{      }|v-v^*| \le \varepsilon\\
			& \text{      }|x-x^*| \le \varepsilon\\
			& \text{      }Sv = 0\\
			& \text{      }v = f(x,p) + e\\
			& \text{      }x_{min}\le x \le x_{max}\\
			& \text{      }p_{min} \le p \le p_{max}			
			\end{align}
		\end{subequations}		
	\end{center}

@@

\end{document}

>>>>

	The optimization formulation to estimate fluxes given below is based on the minimization of the tolerance for the L2-norm of the difference between the model predicted flux and the noisy flux. 
	\begin{center}
		\begin{subequations}\label{eq:noisyopt}
			\begin{align}
			\underset{x,p,e}{\mathrm{min}} & \text{      }e\\
			\mathrm{st} & \text{      }|v-v^*| \le \varepsilon\\
			& \text{      }|x-x^*| \le \varepsilon\\
			& \text{      }Sv = 0\\
			& \text{      }v = f(x,p) + e\\
			& \text{      }x_{min}\le x \le x_{max}\\
			& \text{      }p_{min} \le p \le p_{max}\\	
			& \text{      }e_{min} \le e \le e_{max}						
			\end{align}
		\end{subequations}		
	\end{center}

@@

	\paragraph{Changes in problem formulation due to feasibility issues:}
	Since the above problem (Equation \ref{eq:noisyopt}) does not result in feasible global optimal solutions (using SCIP), the constraints are relaxed and the feasible problem is presented below.

	\begin{center}
		\begin{subequations}\label{eq:optmod}
			\begin{align}
			\underset{x,p_i,e_i}{\mathrm{min}} & \text{      }e_i\\
			\mathrm{st} & \text{      }|v_i-v^*| \le 0.2\\
			& \text{      }|x-x^*| \le 0.3\\
			& \text{      }|Sv| \le 1\text{x}10^{-8}\\
			& \text{      }v_i = f(x,p_i) + e\\
			& \text{      }v_{j\not= i} = f(x,p_{j\not=i})\\
			& \text{      }x_{min}\le x \le x_{max}\\
			& \text{      }p_{i,min} \le p_i \le p_{i,max}\\
			& \text{      }e_{i,min} \le e_i \le e_{i,max}					
			\end{align}
		\end{subequations}		
	\end{center}

	In Equation (\ref{eq:optmod}) above, the index $i$ represents the flux whose parameters are being optimized and index $j$ represents all other fluxes whose parameters are held constant.

	The steady state constraint has been relaxed (from a equality constraint to an inequality constraint) along with permitting the concentrations and the estimated fluxes to deviate significantly from their experimentally observed values (~20 - 30\%).

	The bounds for the flux noise were set at (0,20) in the above problem.
\end{document}
